The Astropy Project:

### 2017-09-29 main.tex
imposing my will

\python\footnote{\url{https://www.python.org/}} is an increasingly
popular general-purpose scripting language that is available under a
permissive open source software licence free of charge for all major
operating systems. Stable and well-developed packages provide support
for array arithmetic \citep[numpy,][]{numpy}, a wide variety of
functions for scientific computing \citep[scipy,][]{numpy}, and
publication-quality plotting \citep[matplotlib,][]{matplotlib}. Tens of
thousands of other packages are available which can help with tasks
that are not astronomy specific but might be performed in the course
of astronomical research, e.g.\ presenting results on websites or
interfacing with databases.

@@

The first public release of the \astropy\ package is described in
\cite{2013A&A...558A..33A}. Since then, the \astropy\ package has been
used in hundreds of projects, and the scope of the package as grown
considerably. At the same time, the community of astronomers
contributing to the project has grown tremendously and an ecosystem
of packages supporting or affiliated with the \astropy\ core has
developed. In this paper, we describe the current status of the
\astropy\ community, the \astropy\ core package, and the \astropy\
ecosystem.

We start by describing the way the \astropy\ project works and is
organized in section~\ref{sec:concepts}.  The project develops a core
package called \astropypkg\ (section~\ref{sec:core}) and several
separate packages that help setting up the infrastructure for testing,
documentation etc.\ (section~\ref{sec:infrastructure}). In
section~\ref{sec:learning} we give an overview of the wealth of
resources created to teach new users the use of the \astropy\ packages
and how to contribute to the community. We end with a short vision for
the future of \astropy\ in section~\ref{sec:future}.

>>>>

\python\footnote{\url{https://www.python.org/}} is an increasingly popular
general-purpose scripting language that is available under a permissive open
source software licence free of charge for all major operating systems. Stable
and well-developed packages provide support for array arithmetic
\citep[\package{numpy},][]{numpy}, a wide variety of functions for scientific
computing \citep[\package{scipy},][]{numpy}, and publication-quality plotting
\citep[\package{matplotlib},][]{matplotlib}. Tens of thousands of other packages
are available which can help with tasks that are not astronomy specific but
might be performed in the course of astronomical research, e.g., presenting
results on websites or interfacing with databases.

@@

The first public release of the \astropy\ package is described in
\cite{astropy}. Since then, the \astropy\ package has been
used in hundreds of projects, and the scope of the package as grown
considerably. At the same time, the community of astronomers
contributing to the project has grown tremendously and an ecosystem
of packages supporting or affiliated with the \astropy\ core has
developed. In this paper, we describe the current status of the
\astropy\ community, the \astropy\ core package, and the \astropy\
ecosystem.

We start by describing the way the \astropy\ project works and is
organized in \sectionname~\ref{sec:concepts}.  The project develops a core
package called \astropypkg\ (\sectionname~\ref{sec:core}) and several
separate packages that help setting up the infrastructure for testing,
documentation etc.\ (\sectionname~\ref{sec:infrastructure}). In
\sectionname~\ref{sec:learning} we give an overview of the wealth of
resources created to teach new users the use of the \astropy\ packages
and how to contribute to the community. We end with a short vision for
the future of \astropy\ in \sectionname~\ref{sec:future}.
